Variance in scarid grazing behavior across Caribbean reef sites

### 2021-01-09 r/old drafts/Paper_analyses_medians.Rmd
file organization

g <- arrangeGrob(
  arrangeGrob(fr_qup, fr_stop, gfrac_qup, gfrac_stop, br_qup, br_stop, fi_qup, fi_stop, ncol=2, heights = c(1,1,1,1.5)), 
              arrangeGrob(legend), 
              ncol=2, widths = c(5,1))

ggsave(here("figs/behavior_panel.png"),g)
```

## Kruskal-Wallis tests
```{r}
vir <- sum_id %>% filter(species_code == "stop")
vet <- sum_id %>% filter(species_code == "qup")

kruskal.test(fr ~ site, data = vet) # p<0.001
kruskal.test(fr ~ site, data = vir) # p<0.001

kruskal.test(br ~ site, data = vet) # p>0.5 (p=0.63)
kruskal.test(br ~ site, data = vir) # p>0.5 (p=0.55)

kruskal.test(g_frac ~ site, data = vet) # p<0.001
kruskal.test(g_frac ~ site, data = vir) # p<0.001

kruskal.test(for_bites ~ site, data = vet) # p<0.001
kruskal.test(for_bites ~ site, data = vir) # p<0.001
```

>>>>

g <- arrangeGrob(
  arrangeGrob(fr_qup, fr_stop, gfrac_qup, gfrac_stop, br_qup, br_stop, fi_qup, fi_stop, ncol=2, heights = c(1,1,1,2)), 
              arrangeGrob(legend), 
              ncol=2, widths = c(5,1))
plot(g)
ggsave(here("figs/behavior_panel.png"),g)
```

```{r}
# indv plots for slides

library(ggpubr)
library(ggtext)

fr_qup <- 
  ggplot(filter(sum_ssp_sub, species_code == "qup"), 
         aes(x=factor(site, levels = sum_site$site), y=fr_median)) +
  geom_bar(stat = "identity", aes(fill = island), position = "dodge") +
  geom_errorbar(aes(ymin=fr_median-fr_se, ymax=fr_median+fr_se), width=.2,
                 position=position_dodge(.9)) +
  scale_fill_brewer(palette = "Blues", name = "Island") +
  labs(y = "", 
       title = "*S. vetula* (queen parrotfish)") +
  theme_bw() + 
  theme(plot.title = element_markdown(hjust = 0.5),
        plot.margin = margin(5, 0, 0, 5, unit = "pt"),
        strip.text = element_text(face = "italic"), 
        axis.text.x = element_text(angle = 45, hjust = 1),
        axis.title.x = element_blank()
        )

fr_stop <- 
  ggplot(filter(sum_ssp_sub, species_code == "stop"), 
         aes(x=factor(site, levels = sum_site$site), y=fr_median)) +
  geom_bar(stat = "identity", aes(fill = island), position = "dodge") +
  geom_errorbar(aes(ymin=fr_median-fr_se, ymax=fr_median+fr_se), width=.2,
                 position=position_dodge(.9)) +
  scale_fill_brewer(palette = "Blues", name = "Island") +
  labs(y = expression(Feeding~rate~(bites~min^-1)),
       title = "*S. viride* (stoplight parrotfish)") +
  theme_bw() + 
  theme(plot.title = element_markdown(hjust = 0.5),
        plot.margin = margin(5, 4, 0, 0, unit = "pt"),
        strip.text = element_text(face = "italic"), 
        axis.text.x = element_text(angle = 45, hjust = 1),
        axis.title.x = element_blank(),
        axis.title.y = element_text(size=10)
        )

ggarrange(fr_stop, fr_qup, 
          #abels = c("A", "B"),
          ncol = 2, nrow = 1,
          common.legend = TRUE, legend = "right")

ggsave(here("figs", "fr.png"), height = 4, width = 8)

fi_qup <- 
  ggplot(filter(sum_ssp_sub, species_code == "qup"), 
         aes(x=factor(site, levels = sum_site$site), y=for_bites_median)) +
  geom_bar(stat = "identity", aes(fill = island), position = "dodge") +
  geom_errorbar(aes(ymin=for_bites_median-for_bites_se, ymax=for_bites_median+for_bites_se), width=.2,
                 position=position_dodge(.9)) +
  scale_fill_brewer(palette = "Blues", name = "Island") +
  labs(y = "", 
       title = "*S. vetula* (queen parrotfish)") +
  theme_bw() + 
  theme(plot.title = element_markdown(hjust = 0.5),
        plot.margin = margin(5, 0, 0, 5, unit = "pt"),
        strip.text = element_text(face = "italic"), 
        axis.text.x = element_text(angle = 45, hjust = 1),
        axis.title.x = element_blank()
        )

fi_stop <- 
  ggplot(filter(sum_ssp_sub, species_code == "stop"), 
         aes(x=factor(site, levels = sum_site$site), y=for_bites_median)) +
  geom_bar(stat = "identity", aes(fill = island), position = "dodge") +
  geom_errorbar(aes(ymin=for_bites_median-for_bites_se, ymax=for_bites_median+for_bites_se), width=.2,
                 position=position_dodge(.9)) +
  scale_fill_brewer(palette = "Blues", name = "Island") +
  labs(y = expression(Grazing~intensity~(bites~foray^-1)),
       title = "*S. viride* (stoplight parrotfish)") +
  theme_bw() + 
  theme(plot.title = element_markdown(hjust = 0.5),
        plot.margin = margin(5, 4, 0, 0, unit = "pt"),
        strip.text = element_text(face = "italic"), 
        axis.text.x = element_text(angle = 45, hjust = 1),
        axis.title.x = element_blank(),
        axis.title.y = element_text(size=10)
        )

ggarrange(fi_stop, fi_qup, 
          #abels = c("A", "B"),
          ncol = 2, nrow = 1,
          common.legend = TRUE, legend = "right")

ggsave(here("figs", "fi.png"), height = 4, width = 8)
```

Kruskal-Wallis tests to look at significance of inter-site variance for different behavioral variables:

Feeding rate:
```{r}
vir <- sum_id %>% filter(species_code == "stop")
vet <- sum_id %>% filter(species_code == "qup")

kruskal.test(fr ~ site, data = vet) # p<0.001
kruskal.test(fr ~ site, data = vir) # p<0.001
```

Bite rate:
```{r}
kruskal.test(br ~ site, data = vet) # p>0.5 (p=0.63)
kruskal.test(br ~ site, data = vir) # p>0.5 (p=0.55)
```

Fraction of time grazing:
```{r}
kruskal.test(g_frac ~ site, data = vet) # p<0.001
kruskal.test(g_frac ~ site, data = vir) # p<0.001
```

Grazing intensity:
```{r}
kruskal.test(for_bites ~ site, data = vet) # p<0.001
kruskal.test(for_bites ~ site, data = vir) # p<0.001
```

All significant (p < 0.001) except for fraction of time spent grazing.
